PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
changed mhq to mhd

```{r glad gad cleaning}
glad.gad.raw.id <- glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen,
    gad.feeling_nervous_anxious_or_on_edge_prepan_numeric = gad.feeling_nervous_anxious_or_on_edge_numeric,
    gad.control_worrying_stop_prepan_numeric = gad.control_worrying_stop_numeric,
    gad.worrying_too_much_about_different_things_prepan_numeric = gad.worrying_too_much_about_different_things_numeric,
    gad.trouble_relaxing_prepan_numeric = gad.trouble_relaxing_numeric,
    gad.sit_restless_hard_prepan_numeric = gad.sit_restless_hard_numeric,
    gad.becoming_easily_annoyed_or_irritable_prepan_numeric = gad.becoming_easily_annoyed_or_irritable_numeric,
    gad.awful_feeling_afraid_happen_prepan_numeric = gad.awful_feeling_afraid_happen_numeric
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

# glad mhq

```{r glad mhq cols}
glad.mhq.raw <- readRDS(file = paste0(data.raw_path,"/glad/mhq_glad.rds"))
dim(glad.mhq.raw)
colnames(glad.mhq.raw)
```

```{r glad mhq cleaning}
glad.mhq.raw.id <- glad.mhq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhq.")
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.mhq.raw.id)
# Inspect colnames
colnames(glad.mhq.raw.id)
#Differences
dim(glad.mhq.raw)[1]-dim(glad.mhq.raw.id)[1]
```

@@

```{r glad mhq depressive_disorders}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    depressive_disorders_numeric =
      case_when(
        (mhq.depression_numeric == "0" &
        (mhq.pregnancy_depression_numeric == "0" | is.na(mhq.pregnancy_depression_numeric)) & 
        (mhq.premenstrual_dysphoric_disorder_pmdd_numeric == "0" | is.na(mhq.premenstrual_dysphoric_disorder_pmdd_numeric))) ~ 0,
        mhq.depression_numeric == "1" ~ 1,
        mhq.pregnancy_depression_numeric == "1" ~ 1,
        mhq.premenstrual_dysphoric_disorder_pmdd_numeric == "1" ~ 1))

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    depressive_disorders =
      recode_factor(depressive_disorders_numeric,
                    "0" = "No depressive disorder",
                    "1" = "Depressive disorder",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(depressive_disorders)
```

```{r Check depressive_disorders}
glad.mhq.raw.id %>%
  select(
    depressive_disorders,
    depressive_disorders_numeric,
    mhq.depression_numeric,
    mhq.pregnancy_depression_numeric,
    mhq.premenstrual_dysphoric_disorder_pmdd_numeric,
    mhq.depression,
    mhq.pregnancy_depression,
    mhq.premenstrual_dysphoric_disorder_pmdd
  )
```

Anxiety disorders group
```{r glad mhq anxiety_disorders}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    anxiety_disorders_numeric =
      case_when(
        mhq.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
        mhq.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
        mhq.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
        mhq.agoraphobia_numeric == "1" ~ 1,
        mhq.panic_disorder_numeric == "1" ~ 1,
        mhq.panic_attacks_numeric == "1" ~ 1,
        (mhq.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
        mhq.social_anxiety_or_social_phobia_numeric == "0" &
        mhq.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
        mhq.agoraphobia_numeric == "0" &
        mhq.panic_disorder_numeric == "0" &
        mhq.panic_attacks_numeric == "0") ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    anxiety_disorders =
      recode_factor(anxiety_disorders_numeric,
                    "0" = "No anxiety disorder",
                    "1" = "Anxiety disorder",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(anxiety_disorders)
```

```{r Check anxiety_disorders}
glad.mhq.raw.id %>%
  select(
    anxiety_disorders,
    anxiety_disorders_numeric,
    mhq.anxiety_nerves_or_generalised_anxiety_disorder_numeric,
    mhq.social_anxiety_or_social_phobia_numeric,
    mhq.specific_phobia_e.g._phobia_of_flying_numeric,
    mhq.agoraphobia_numeric,
    mhq.panic_disorder_numeric,
    mhq.panic_attacks_numeric,
    mhq.anxiety_nerves_or_generalised_anxiety_disorder,
    mhq.social_anxiety_or_social_phobia,
    mhq.specific_phobia_e.g._phobia_of_flying,
    mhq.agoraphobia,
    mhq.panic_disorder,
    mhq.panic_attacks
  )
```

Agoraphonia and panic disorder group
```{r glad mhq agoraphobia_panic_disorder}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    agoraphobia_panic_disorder_numeric =
      case_when(
        mhq.agoraphobia_numeric == "1" ~ 1,
        mhq.panic_disorder_numeric == "1" ~ 1,
        mhq.panic_attacks_numeric == "1" ~ 1,
        (mhq.agoraphobia_numeric == "0" &
        mhq.panic_disorder_numeric == "0" &
        mhq.panic_attacks_numeric == "0") ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    agoraphobia_panic_disorder =
      recode_factor(agoraphobia_panic_disorder_numeric,
                    "0" = "No agoraphobia/panic disorder",
                    "1" = "Agoraphobia/panic disorder",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(agoraphobia_panic_disorder)
```

```{r Check agoraphobia_panic_disorder}
glad.mhq.raw.id %>%
  select(
    agoraphobia_panic_disorder,
    agoraphobia_panic_disorder_numeric,
    mhq.agoraphobia_numeric,
    mhq.panic_disorder_numeric,
    mhq.panic_attacks_numeric,
    mhq.agoraphobia,
    mhq.panic_disorder,
    mhq.panic_attacks
  )
```

Eating disorders group
```{r glad mhq eating_disorders}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhq.anorexia_nervosa_numeric == "1" ~ 1,
        mhq.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhq.bulimia_nervosa_numeric == "1" ~ 1,
        mhq.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
        (mhq.anorexia_nervosa_numeric == "0" &
        mhq.atypical_anorexia_nervosa_numeric == "0" &
        mhq.bulimia_nervosa_numeric == "0" &
        mhq.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    eating_disorders =
      recode_factor(eating_disorders_numeric,
                    "0" = "No eating disorder",
                    "1" = "Eating disorder",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(eating_disorders)
```

```{r Check eating_disorders}
glad.mhq.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    mhq.anorexia_nervosa_numeric,
    mhq.atypical_anorexia_nervosa_numeric,
    mhq.bulimia_nervosa_numeric,
    mhq.psychological_overeating_or_bingeeating_numeric,
    mhq.anorexia_nervosa,
    mhq.atypical_anorexia_nervosa,
    mhq.bulimia_nervosa,
    mhq.psychological_overeating_or_bingeeating
  )
```

Obsessive compulsive disorders
```{r glad mhq obsessive_compulsive_disorders}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    obsessive_compulsive_disorders_numeric =
      case_when(
        mhq.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
        mhq.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
        mhq.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
        (mhq.obsessivecompulsive_disorder_ocd_numeric == "0" &
        mhq.obsessive_compulsive_related_disorders_numeric == "0" &
        mhq.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    obsessive_compulsive_disorders =
      recode_factor(obsessive_compulsive_disorders_numeric,
                    "0" = "No obsessivecompulsive disorder",
                    "1" = "Obsessive compulsive disorder",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(obsessive_compulsive_disorders)
```

```{r Check obsessive_compulsive_disorders}
glad.mhq.raw.id %>%
  select(
    obsessive_compulsive_disorders,
    obsessive_compulsive_disorders_numeric,
    mhq.obsessivecompulsive_disorder_ocd,
    mhq.obsessivecompulsive_disorder_ocd_numeric,
    mhq.obsessive_compulsive_related_disorders,
    mhq.obsessive_compulsive_related_disorders_numeric
  )
```

Psychotic disorders group
```{r glad mhq psychotic_disorders}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    psychotic_disorders_numeric =
      case_when(
        mhq.schizophrenia_numeric == "1" ~ 1,
        mhq.schizoaffective_disorder_numeric == "1" ~ 1,
        mhq.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
        (mhq.schizophrenia_numeric == "0" &
        mhq.schizoaffective_disorder_numeric == "0" &
        mhq.type_psychosis_psychotic_illness_numeric == "0") ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    psychotic_disorders =
      recode_factor(psychotic_disorders_numeric,
                    "0" = "No psychotic disorder",
                    "1" = "Psychotic disorder",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(psychotic_disorders)
```

```{r Check psychotic_disorders}
glad.mhq.raw.id %>%
  select(
    psychotic_disorders,
    psychotic_disorders_numeric,
    mhq.schizophrenia_numeric,
    mhq.schizoaffective_disorder_numeric,
    mhq.type_psychosis_psychotic_illness_numeric,
    mhq.schizophrenia,
    mhq.schizoaffective_disorder,
    mhq.type_psychosis_psychotic_illness
  )
```

Overlap between self-report schizphrenia and bipolar
+++CH: Check overlap between schizophrenia group and bipolar disorder
++KT: Only 63 with comorbid sel-report bipolar and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
```{r check bipolar overlap with schizophrenia}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    bipolar_and_schizophrenia_numeric =
      if_else(
        mhq.schizophrenia_numeric == "1" &
          mhq.mania_hypomania_bipolar_or_manicdepression_numeric == "1", 1, 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    bipolar_and_schizophrenia =
      recode_factor(bipolar_and_schizophrenia_numeric,
                    "0" = "No comorbid bipoar and schizophrenia",
                    "1" = "Comorbid bipoar and schizophrenia",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(bipolar_and_schizophrenia)
```

Personality disorder groups
++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
Cluster A
1. Paranoid                         28 ( 1.0%)
2. Schizoid                         15 ( 0.5%)
3. Schizotypal                      14 ( 0.5%)
```{r glad mhq personality_cluster_a}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    personality_cluster_a_numeric =
      case_when(
        mhq.personality_disorder_diagnosed_numeric == "1" ~ 1,
        mhq.personality_disorder_diagnosed_numeric == "2" ~ 1,
        mhq.personality_disorder_diagnosed_numeric == "3" ~ 1,
        mhq.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhq.personality_disorder_numeric == "0" ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    personality_cluster_a =
      recode_factor(personality_cluster_a_numeric,
                    "0" = "No personality disorder cluster A",
                    "1" = "Personality disorder cluster A",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(personality_cluster_a)
```

```{r Check personality_cluster_a}
glad.mhq.raw.id %>%
  select(
    personality_cluster_a,
    personality_cluster_a_numeric,
    mhq.personality_disorder_diagnosed,
    mhq.personality_disorder_diagnosed_numeric
  )
```

@@

glad data frame list
```{r glad data frame list}
glad.dfs.list <- list(
  glad.dem.raw.id,
  glad.gad.raw.id,
  glad.mhq.raw.categories,
  glad.ocir.raw.id,
  glad.pcl.raw.id,
  glad.phq.raw.id,
  coping.glad.gad.raw.id,
  coping.glad.pcl.raw.id,
  coping.glad.phq.raw.id,
  coping.glad.ocir.raw.id
)
```

>>>>

```{r glad gad cleaning}
exclude_cols <- c("Sample",
                  "ID")

glad.gad.raw.id <- glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

# glad mhd

```{r glad mhd cols}
glad.mhd.raw <- readRDS(file = paste0(data.raw_path,"/glad/mhd_glad.rds"))
dim(glad.mhd.raw)
colnames(glad.mhd.raw)
```

```{r glad mhd cleaning}
glad.mhd.raw.id <- glad.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd.")
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.mhd.raw.id)
# Inspect colnames
colnames(glad.mhd.raw.id)
#Differences
dim(glad.mhd.raw)[1]-dim(glad.mhd.raw.id)[1]
```

@@

```{r glad mhd depressive_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depressive_disorders_numeric =
      case_when(
        (mhd.depression_numeric == "0" &
        (mhd.pregnancy_depression_numeric == "0" | is.na(mhd.pregnancy_depression_numeric)) & 
        (mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "0" | is.na(mhd.premenstrual_dysphoric_disorder_pmdd_numeric))) ~ 0,
        mhd.depression_numeric == "1" ~ 1,
        mhd.pregnancy_depression_numeric == "1" ~ 1,
        mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "1" ~ 1))

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depressive_disorders =
      recode_factor(depressive_disorders_numeric,
                    "0" = "No depressive disorder",
                    "1" = "Depressive disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(depressive_disorders)
```

```{r Check depressive_disorders}
glad.mhd.raw.id %>%
  select(
    depressive_disorders,
    depressive_disorders_numeric,
    mhd.depression_numeric,
    mhd.pregnancy_depression_numeric,
    mhd.premenstrual_dysphoric_disorder_pmdd_numeric,
    mhd.depression,
    mhd.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd
  )
```

Anxiety disorders group
```{r glad mhd anxiety_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    anxiety_disorders_numeric =
      case_when(
        mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
        mhd.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
        mhd.social_anxiety_or_social_phobia_numeric == "0" &
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
        mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    anxiety_disorders =
      recode_factor(anxiety_disorders_numeric,
                    "0" = "No anxiety disorder",
                    "1" = "Anxiety disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(anxiety_disorders)
```

```{r Check anxiety_disorders}
glad.mhd.raw.id %>%
  select(
    anxiety_disorders,
    anxiety_disorders_numeric,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.agoraphobia_numeric,
    mhd.panic_disorder_numeric,
    mhd.panic_attacks_numeric,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.agoraphobia,
    mhd.panic_disorder,
    mhd.panic_attacks
  )
```

Agoraphonia and panic disorder group
```{r glad mhd agoraphobia_panic_disorder}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    agoraphobia_panic_disorder_numeric =
      case_when(
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    agoraphobia_panic_disorder =
      recode_factor(agoraphobia_panic_disorder_numeric,
                    "0" = "No agoraphobia/panic disorder",
                    "1" = "Agoraphobia/panic disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(agoraphobia_panic_disorder)
```

```{r Check agoraphobia_panic_disorder}
glad.mhd.raw.id %>%
  select(
    agoraphobia_panic_disorder,
    agoraphobia_panic_disorder_numeric,
    mhd.agoraphobia_numeric,
    mhd.panic_disorder_numeric,
    mhd.panic_attacks_numeric,
    mhd.agoraphobia,
    mhd.panic_disorder,
    mhd.panic_attacks
  )
```

Eating disorders group
```{r glad mhd eating_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 1,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    eating_disorders =
      recode_factor(eating_disorders_numeric,
                    "0" = "No eating disorder",
                    "1" = "Eating disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(eating_disorders)
```

```{r Check eating_disorders}
glad.mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.psychological_overeating_or_bingeeating_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.psychological_overeating_or_bingeeating
  )
```

Obsessive compulsive disorders
```{r glad mhd obsessive_compulsive_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders_numeric =
      case_when(
        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
        mhd.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
        mhd.obsessive_compulsive_related_disorders_numeric == "0" &
        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders =
      recode_factor(obsessive_compulsive_disorders_numeric,
                    "0" = "No obsessivecompulsive disorder",
                    "1" = "Obsessive compulsive disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(obsessive_compulsive_disorders)
```

```{r Check obsessive_compulsive_disorders}
glad.mhd.raw.id %>%
  select(
    obsessive_compulsive_disorders,
    obsessive_compulsive_disorders_numeric,
    mhd.obsessivecompulsive_disorder_ocd,
    mhd.obsessivecompulsive_disorder_ocd_numeric,
    mhd.obsessive_compulsive_related_disorders,
    mhd.obsessive_compulsive_related_disorders_numeric
  )
```

Psychotic disorders group
```{r glad mhd psychotic_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    psychotic_disorders_numeric =
      case_when(
        mhd.schizophrenia_numeric == "1" ~ 1,
        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
        (mhd.schizophrenia_numeric == "0" &
        mhd.schizoaffective_disorder_numeric == "0" &
        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    psychotic_disorders =
      recode_factor(psychotic_disorders_numeric,
                    "0" = "No psychotic disorder",
                    "1" = "Psychotic disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(psychotic_disorders)
```

```{r Check psychotic_disorders}
glad.mhd.raw.id %>%
  select(
    psychotic_disorders,
    psychotic_disorders_numeric,
    mhd.schizophrenia_numeric,
    mhd.schizoaffective_disorder_numeric,
    mhd.type_psychosis_psychotic_illness_numeric,
    mhd.schizophrenia,
    mhd.schizoaffective_disorder,
    mhd.type_psychosis_psychotic_illness
  )
```

Overlap between self-report schizphrenia and bipolar
+++CH: Check overlap between schizophrenia group and bipolar disorder
++KT: Only 63 with comorbid sel-report bipolar and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
```{r check bipolar overlap with schizophrenia}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia_numeric =
      if_else(
        mhd.schizophrenia_numeric == "1" &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "1", 1, 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia =
      recode_factor(bipolar_and_schizophrenia_numeric,
                    "0" = "No comorbid bipoar and schizophrenia",
                    "1" = "Comorbid bipoar and schizophrenia",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(bipolar_and_schizophrenia)
```

Personality disorder groups
++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
Cluster A
1. Paranoid                         28 ( 1.0%)
2. Schizoid                         15 ( 0.5%)
3. Schizotypal                      14 ( 0.5%)
```{r glad mhd personality_cluster_a}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    personality_cluster_a_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    personality_cluster_a =
      recode_factor(personality_cluster_a_numeric,
                    "0" = "No personality disorder cluster A",
                    "1" = "Personality disorder cluster A",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(personality_cluster_a)
```

```{r Check personality_cluster_a}
glad.mhd.raw.id %>%
  select(
    personality_cluster_a,
    personality_cluster_a_numeric,
    mhd.personality_disorder_diagnosed,
    mhd.personality_disorder_diagnosed_numeric
  )
```

@@

glad data frame list
```{r glad data frame list}
glad.dfs.list <- list(
  glad.dem.raw.id,
  glad.gad.raw.id,
  glad.mhd.raw.categories,
  glad.ocir.raw.id,
  glad.pcl.raw.id,
  glad.phq.raw.id,
  coping.glad.gad.raw.id,
  coping.glad.pcl.raw.id,
  coping.glad.phq.raw.id,
  coping.glad.ocir.raw.id
)
```
